---
title: "Histogram of Narrated/Remembered Religious Conflicts"
author: "PMB"
date: "12/11/2021"
output: html_document
---

## Histogram of the Narrative Status of Religious Conflicts

First, we set up R Studio.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Next, we load and import the required libraries.

```{r important libraries}

library(gutenbergr)
library(dplyr)
library(tidytext)
library(stringr)
library(tidyverse)
library(tm)
library(ggplot2)
library(tidyr)
library(plotly)
library(ggthemes)
library(scales)
```

Next, we import the CSV file containing the required data for the histogram.

```{r importing csv}
narrativestatus_religiousconflict <-
read_csv("C:/Users/Pulari/Downloads/narrativestatus_religiousconflicts.csv")
```

Now that we have our data, it's time to create our visualization! We will be using the code created by Alex Polymath (for reference: [https://www.codementor.io/\@alexander-k/r-word-frequency-in-dataframe-165jgfxxqe\#step-1-create-stopwords-dataframe](https://www.codementor.io/@alexander-k/r-word-frequency-in-dataframe-165jgfxxqe#step-1-create-stopwords-dataframe){.uri}).

```{r histogram}
ggplot(narrativestatus_religiousconflict, aes(x = narrative_status, y = religious_conflicts, fill= narrative_status )) + geom_col() 

```

As per our analysis of this query in the previous section, most instances of religious conflicts are narrated, and those which are remembered or told follow after a drastic drop in occurrences in descending order.
